\section{Education}\label{education}

\begin{description}
\tightlist
\item[2017]
PhD in Ecology: Environmental Policy and Human Ecology, University of
California, Davis (expected)
\item[2012]
MS in Biology, West Virginia University
\item[2004]
BS in Chemistry, Fort Lewis College
\end{description}

\section{Publications}\label{publications}

\subsection{Refereed Publications}\label{refereed-publications}

\begin{description}
\tightlist
\item[2016]
\textbf{Michael Levy}. gwdegree: Improving interpretation of
geometrically-weighted degree estimates in exponential random graph
models. The Journal of Open Source Software 1(3).
\item[2014]
\textbf{Michael Levy} and Jonathan Cumming. Development of soils and
communities of plants and arbuscular mycorrhizal fungi on West Virginia
surface mines. Environmental Management 54(5): 1153-1162.
\end{description}

\subsection{Manuscripts in Review}\label{manuscripts-in-review}

\begin{description}
\tightlist
\item[\phantom{2016}]
\textbf{Michael Levy} and Mark Lubell. Structural signatures of
cooperation, innovation, and boundary spanning in agriculture knowledge
networks.
\item[\phantom{2016}]
Marco Bastos, Carlo Piccardi, \textbf{Michael Levy}, Neil McRoberts, and
Mark Lubell. Core-periphery or decentralized? How centralized networks
emerge from sharing specialized agriculture information.
\end{description}

\subsection{Manuscripts in
Preparation}\label{manuscripts-in-preparation}

\begin{description}
\tightlist
\item[\phantom{2016}]
\textbf{Michael Levy}, Mark Lubell, Philip Leifeld, and Skyler Cramner.
Use and interpretation of geometrically weighted degree in exponential
random graph models.
\item[\phantom{2016}]
\textbf{Michael Levy}, Patrick Bitterman, Kenny Wallen, Katie Lyon,
Ellen Esch, and Michael Saha. Generation of an empircally based agent
population for a coupled model of fire and homeowner behavior in the
wildland-urban interface.
\item[\phantom{2016}]
Mark Lubell, \textbf{Michael Levy}, Aseem Prakash, and Matt Potoski.
Clubs old and new: Social networks and participation in voluntary
environmental programs.
\end{description}

\subsection{Policy and Outreach
Publications}\label{policy-and-outreach-publications}

\begin{description}
\tightlist
\item[2016]
\textbf{Michael Levy}, Neil McRoberts, and Mark Lubell. Pillars of
sustainable agriculture. Policy brief for UC Division of Agriculture and
Natural Resources.
\item[2016]
\textbf{Michael Levy}, Neil McRoberts, and Mark Lubell. Mental models of
sustainable agriculture. Policy brief for UC Division of Agriculture and
Natural Resources.
\item[2015]
\textbf{Michael Levy} and Matthew Hoffman. Lodi rules for sustainable
winegrowing certification program, 2015 report.
\item[2013]
\textbf{Michael Levy}. Integrating science, management, and policy for
the future of water in California. Eos, 94(29): 256.
\item[2013]
\textbf{Michael Levy}, Matthew Hoffman, Vicken Hillis, and Mark Lubell.
Sustainability certification: Why do vineyards participate? Policy Brief
for UC Davis Policy Institute for Energy, Environment and the Economy.
\item[2013]
\textbf{Michael Levy}. Measure I is our best option for necessary water
improvements. The Davis Enterprise, February 10, 2013: A15.
\item[2010 - 2012]
\textbf{Michael Levy}. Weekly environmental science and policy opinion
column. The Daily Athenaeum, 124(12) - 125(94).
\end{description}

\section{Awards}\label{awards}

\begin{description}
\tightlist
\item[2016]
Fire on the Fringe: A coupled agent-based model of homeowner and
wildfire behavior in Southern California, National Socio-Environmental
Synthesis Center (SESYNC) Graduate Research Fellow, \$2,000.
\item[2016]
Improving statistical inference on networks, Amazon Web Services Cloud
Credits for Research Grant, \$703.
\item[2016]
Political Networks Conference Travel Grant, \$900.
\item[2015]
Professors for the Future Fellowship, \$3,000.
\item[2014]
Sustainable Agriculture Scholarship, Annie's Homegrown, \$2,500.
\item[2014]
Henry A. Jastro Research Award, UC Davis College of Agricultural and
Environmental Sciences, \$1,500.
\item[2012]
Climate Change, Water, and Society, Integrative Graduate Education
Research Traineeship, National Science Foundation, \$115,000.
\item[2012]
Ecology Fellowship, UC Davis, \$51,000.
\item[2011]
Graduate Student Policy Award, Ecological Society of America.
\item[2009]
HERF Supplementary Fellowship, West Virginia University, \$2,000.
\end{description}

\section{Presentations}\label{presentations}

\subsection{Professional Conferences}\label{professional-conferences}

\begin{description}
\tightlist
\item[2016]
\textbf{Michael Levy}. Teaching R to 200 people in a week. International
R User Conference, Stanford, CA.
\item[2016]
\textbf{Michael Levy}, Mark Lubell, Philip Leifeld, Skyler Cranmer.
Interpretation of geometrically weighted degree estimates in exponential
random graph models. Political Networks Conference, Saint Louis, MO.
\item[2016]
\textbf{Michael Levy}. Mental models of sustainable agriculture. Duck
Family Graduate Workshop on Environmental Politics and Governance,
Seattle, WA.
\item[2016]
\textbf{Michael Levy}, Mark Lubell, Philip Leifeld, Skyler Cranmer.
Estimating and interpreting geometrically weighted statistics in
exponential random graph models. Midwest Political Science Association
Conference, Chicago, IL.
\item[2016]
\textbf{Michael Levy}. Mental models of sustainable agriculture. Sunbelt
Social Network Conference, Newport Beach, CA.
\item[2015]
\textbf{Michael Levy} and Mark Lubell. Innovation and cooperation in the
structure of agriculture information networks. American Political
Science Association Annual Meeting, San Francisco, CA.
\item[2015]
\textbf{Michael Levy} and Mark Lubell. Innovation and cooperation in
agricultural information networks. Political Networks Conference,
Portland, OR.
\item[2015]
\textbf{Michael Levy}. Cultural multilevel selection and social networks
in sustainable viticulture. Biennial Global Conference: International
Association for the Study of the Commons, Edmonton, AB.
\item[2014]
\textbf{Michael Levy}. Cultural diffusion and polarization: An
agent-based model. Center for Advanced Modeling Graduate Workshop,
Baltimore, MD.
\item[2014]
\textbf{Michael Levy}, Matthew Hoffman, Vicken Hillis, and Mark Lubell.
Who joins the club? Learning pathways for sustainable agriculture
certification. Environmental Politics Conference, Santa Barbara, CA.
\item[2011]
\textbf{Michael Levy} and Jonathan Cumming. Development of soil,
biodiversity, and arbuscular mycorrhizae on pasture-reclaimed surface
mines in Appalachia. Annual Meeting of the Ecological Society of
America, Austin, TX.
\end{description}

\subsection{Outreach Presentations}\label{outreach-presentations}

\begin{description}
\tightlist
\item[2016]
\textbf{Michael Levy}. Automation, lapply, and custom functions in R.
Davis R Users' Group, Davis, CA.
\item[2015]
\textbf{Michael Levy}. Exponential random graph models for statistical
inference on networks. Statistical Sciences Symposium, UC Davis
Department of Statistics, Davis, CA.
\item[2015]
\textbf{Michael Levy}. Predicting interdependence: Inference from
exponential random graph models of social networks. Statistical
Methodology in the Social Sciences Conference, UC Davis Institute for
Social Sciences, Davis, CA.
\item[2015]
\textbf{Michael Levy}. ERGM tutorial. UC Davis Interdisciplinary Network
Science Group, Davis, CA.
\item[2014]
\textbf{Michael Levy}. Environmental certifications among
viticulturists. Lodi Winegrape Commission, Davis, CA.
\item[2014]
\textbf{Michael Levy}. dplyr: Data manipulation in R made easy. Davis R
Users' Group, Davis, CA.
\item[2012]
\textbf{Michael Levy}. Stripping wild and wonderful: Truths and myths
about surface mining in West Virginia. Science on Tap public science
forum, Morgantown, WV.
\item[2011]
\textbf{Michael Levy} and Terence Houston. Weighing the long-term
implications of mountaintop removal mining. Ecological Society of
America podcast, The Ecologist Goes To Washington.
\item[2011]
Bob Baber, Ted Boettner, \textbf{Michael Levy}, and Jeff Skousen. Coal:
The lifeblood of West Virginia? Democracy Matters panel discussion,
Morgantown, WV.
\end{description}

\section{Teaching Experience}\label{teaching-experience}

\subsection{University of California,
Davis}\label{university-of-california-davis}

\begin{description}
\tightlist
\item[2016]
Teaching Assistant, Statistical Rethinking: PhD-level course on applied
computational Bayesian data analysis, with Richard McElreath.
\item[2015]
Developer and Instructor, R Bootcamp: Week-long intensive introduction
to the statistical programming language R for 200 graduate students and
postdoctoral scholars.
\item[2013]
Organizer and Lead, Seminar on agent-based models for the study of
coupled human and natural systems.
\end{description}

\subsection{Software and Data
Carpentry}\label{software-and-data-carpentry}

\begin{description}
\tightlist
\item[2016]
Developer and Co-Instructor, Pilot Social Sciences Data Carpentry
Workshop, UC Davis.
\item[2016]
Co-Instructor, Software Carpentry Workshop, Stanford University.
\item[2016]
Co-Instructor, Software Carpentry Workshop, UC Davis.
\item[2015]
Co-Instructor, Data Carpentry Workshop, UC Davis.
\end{description}

\subsection{Interuniversity Consortium for Political and Social Research
(ICPSR)}\label{interuniversity-consortium-for-political-and-social-research-icpsr}

\begin{description}
\tightlist
\item[2015]
Teaching Assistant, Introduction to Social Network Analysis in R, with
Lorien Jasny.
\end{description}

\subsection{West Virginia University}\label{west-virginia-university}

\begin{description}
\tightlist
\item[2011]
Teaching Assistant, Environmental Biology Laboratory.
\item[2010 - 2011]
Teaching Assistant, Total Science Experience: Mentored small group
research projects from proposal to presentation.
\item[2009 - 2010]
Teaching Assistant, Principles of Biology Laboratory.
\end{description}

\subsection{Other}\label{other}

\begin{description}
\tightlist
\item[2008 - 2009]
English as a Foreign Language Teacher, Dogye Elementary School,
Gangwon-do, South Korea.
\item[2007 - 2008]
MCAT Instructor, The Princeton Review, Boulder CO.
\item[2005 - 2006]
English as a Foreign Language Teacher, Han Yun Sik English Academy,
Busan South Korea.
\end{description}

\section{Additional Education}\label{additional-education}

\begin{description}
\tightlist
\item[2016]
Text Analytics, Interuniversity Consortium for Political and Social
Research, Ann Arbor, MI.
\item[2015]
Seminar on College Teaching, Center for Educational Effectiveness,
Davis, CA.
\item[2015]
Instructor training, Software Carpentry, Davis, CA.
\item[2013]
Multi-platform International Summer School on Agent-Based Modeling and
Simulation, Cirad, Montpellier, France.
\item[2011]
Becoming the Messenger: Science communication training, National Science
Foundation, Morgantown, WV.
\item[2011]
Lobbying Congress for Science, Biological Ecological Sciences Coalition,
Washington DC.
\end{description}

\section{Service}\label{service}

\subsection{UC Davis}\label{uc-davis}

\begin{description}
\tightlist
\item[2015 -]
Co-Administrator, Davis R Users' Group.
\item[2015 -]
Founder \& Administrator, Interdisciplinary Network Science Group.
\item[2014 -]
Maintainer, Statistics Courses Guide, Ecology Graduate Student
Association.
\item[2013 -]
Member, Admissions Committee, Graduate Group in Ecology.
\item[2015]
Graduate Student Representative, Climate Policy Faculty Search
Committee, Department of Environmental Science and Policy.
\item[2015]
Mentor, Dustan Li Undergraduate Research Project.
\item[2013]
Mentor, AggieMentors high school student research program.
\item[2013]
Co-organizer, Future of Water in California Conference.
\item[2013]
Delegate, UC Day in DC.
\end{description}

\subsection{West Virginia University}\label{west-virginia-university-1}

\begin{description}
\tightlist
\item[2010 - 2011]
Mentor, Kylen Whipp Undergraduate Honors Thesis.
\end{description}
